### 2016-12-20 paper.tex
Even less macros
Clean up of interval 1

\usepackage{cite}
\usepackage{hyperref} % \url{url} \href{url}{displayed text}

\usepackage[pdftex]{graphicx}
\graphicspath{{pic/}}
\usepackage{tikz}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
\usepackage{physics}

@@

\newcommand{\mcF}{\mathcal{F}}
\newcommand{\mcH}{\mathcal{H}} % ???
\newcommand{\mcI}{\mathcal{I}}
\newcommand{\mcL}{\mathcal{L}} % L2 space
\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\mcP}{\mathcal{P}}

\newcommand{\bbC}{\mathbb{C}} % complex plane
\newcommand{\bbD}{\mathbb{D}} % complex unit disk
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\bbK}{\mathbb{K}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbT}{\mathbb{T}} % complex unit circle
\newcommand{\bbZ}{\mathbb{Z}}
\newcommand{\bbH}{\mathbb{H}}

@@

\newcommand{\eps}{\varepsilon}

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\renewcommand{\phi}{\varphi} % TODO is there a prettier way to do that

@@

\DeclareMathOperator\atanh{atanh}

@@

Another important property we are going to use is that Cayley transform preserves circles. In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $C(r)$ and radius $R(r)$, where:

\begin{equation}\label{eq:c_and_r}
\begin{aligned}
   C(r) &= \Im \frac{w(r) + w(-r)}{2}
\\ R(r) &= \Im \frac{w(r) - w(-r)}{2}
\end{aligned}
\end{equation}

From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$, which intuinively makes sense since a complex unit circle maps to a real axis. TODO ???

@@

\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}
TODO: $C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$

@@

Let's investigate the model on \autoref{fig:res_bundle}. Schrodinger's operator is defined on edges of the graph as  $-\dv[2]{\psi}{x}$. At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:

@@

Let's use Cauchy–Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, to be precise, it's $\mcL^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

@@

Let's compute an upper bound for the integrand (\ref{eq:int_f}). Note that for $C - R \le y \le \frac{V}{4}$:
\begin{align*}
       & \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\end{align*}

Now, we use a well known inequality which holds for $x > -1$: TODO REFERENCE
\[
\frac{x}{1 + x} \le \ln (1 + x)
\]
, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
\begin{align*}
       & \dots 
\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ = & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}} \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
\end{align*}

Note that we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$. Now the integrand (TODO ACTUALLY ONLY ONE PART OF IT) has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ (TODO WHY) и $b > 0$. That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and strictly increasing, since:
\[
  \left(\frac{y^2}{a + b y}\right)'
= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
= \frac{2y (a + by) - b y^2}{(a + by)^2}
= \frac{y (2a + by)}{(a + by)^2}
\ge 0
\]

This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} = \mcO\left(\frac{1}{R}\right)
\]
TODO ELABORATE ON THAT!

The remaning part of integral is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - C + R} = \mcO(1)
\]

And finally, after combining all these estimages, we get $\mcO(1) \mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$ TODO EXPAND IN TERMS OF small r!

>>>>

\usepackage{cite}
\usepackage{hyperref} % \autoref

\usepackage[pdftex]{graphicx}
\graphicspath{{pic/}}
\usepackage{tikz}

\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
\usepackage{mathtools}

@@

\newcommand{\mcL}{\mathcal{L}} % L2 space
\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\bbC}{\mathbb{C}} % complex plane
\newcommand{\bbD}{\mathbb{D}} % complex unit disk
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbT}{\mathbb{T}} % complex unit circle
\newcommand{\bbH}{\mathbb{H}} % complex upper half plane

@@

% \renewcommand{\Re}{\operatorname{Re}}
% \renewcommand{\Im}{\operatorname{Im}}

@@

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator\asin{asin}
\DeclareMathOperator\atanh{atanh}

@@

Another important property we are going to use is that Cayley transform preserves circles. In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:

\begin{equation}\label{eq:c_and_r}
\begin{aligned}
   C(r) &= \Im \frac{w(r) + w(-r)}{2} = \frac{1 + r^2}{1 - r^2}
\\ R(r) &= \Im \frac{w(r) - w(-r)}{2} = \frac{2 r}{1 - r^2}
\end{aligned}
\end{equation}

From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$, which intuinively makes sense since a complex unit circle maps to a real axis.

Also, we'll note two useful facts:
\begin{itemize}
\item $C(r) - R(r) > 0$
\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
\end{itemize}

% TODO: $C(r) + R(r) = \Im w(r) = \frac{1 + r}{1 - r}$, $C(r) - R(r) = \Im w(-r) = \frac{1 - r}{1 + r}$

@@

\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}

@@

Let's investigate the model on \autoref{fig:res_bundle}. Schrodinger's operator is defined on edges of the graph as  $-\frac{d^2 \psi}{dx^2}$. At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:

@@

Let's use Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, to be precise, it's $\mcL^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

@@

Let's compute an upper bound for the integrand (\ref{eq:int_f}). Note that for $C - R \le y \le \frac{V}{4}$:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\end{align*}

Now, we use a well known inequality which holds for $x > -1$: TODO REFERENCE
\[
\frac{x}{1 + x} \le \ln (1 + x)
\]
, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
\begin{align*}
       & \dots 
\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ =   & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}}  \int \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
\end{align*}

It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).

The first part of the integrand has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ and $b > 0$. That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and non decreasing, since:
\[
  \left(\frac{y^2}{a + b y}\right)'
= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
= \frac{2y (a + by) - b y^2}{(a + by)^2}
= \frac{y (2a + by)}{(a + by)^2}
\ge 0
\]

This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
\]

Interal of the second part of the integrand is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
\]

And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.
